Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-08-18 surfaces-write-up/surface-write-up.tex
mentioened degree leq 0 case

\section{Canonical Rings of Projective Space}
\label{sec:proj}
Let $\bk$ be a field and let $\bp^m$ denote $m$-dimensional
projective space over $\bk$. In this section, we bound the degrees
of generators and relations for divisors
on $\bp^m$, for all $m \geq 1$ in Theorem
~\ref{thm:proj-effective-intro}. 
The $\bp^1$ case restricts to the results of
\cite{dorney:canonical}. We also give an explicit description of the
generators of the canonical ring $R_D$ when $D$ is an effective divisor in Theorem ~\ref{thm:proj-generators-relations}

@@

>>>>

\section{Canonical Rings of Projective Space}
\label{sec:proj}
Let $\bk$ be a field and let $\bp^m$ denote $m$-dimensional
projective space over $\bk$. In this section, we bound the degrees
of generators and relations for divisors
on $\bp^m$, for all $m \geq 1$ in Theorem
~\ref{thm:proj-effective-intro}.
Note that if $\deg D < 0$ the
canonical ring is concentrated in degree 0, and if
$\deg D = 0$, then the canonical ring has a single
generator. Therefore, for the remainder of this section,
we shall assume $\deg D > 0$.
The $\bp^1$ case restricts to the results of
\cite{dorney:canonical}. We also give an explicit description of the
generators of the canonical ring $R_D$ when $D$ is an effective divisor in Theorem ~\ref{thm:proj-generators-relations}

@@

Furthermore, similarly to the case of projective space, 
we will restrict to the case that $D$ is a divisor
for which both of its bi-degrees are positive. We now justify this
restriction. If either of the bidegrees of $D$ are negative,
then the canonical ring is concentrated in degree 0. If one of the
bidegrees is 0, say the first one is 0, then $R_D$ is isomorphic
to $R_{D'}$, where $D' \in \bq \otimes_\bq \di \bp^1$, 
where $D'$ can be written as a sum of divisors whose degrees
are multiples of the second bidegree of $D$. Since the case of
$\bp^1$ has already been analyzed in \cite{canonical:dorney}, we
are justified in assuming that both bi-degrees of $D$ are positive.
